---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# shi18ny

<!-- badges: start -->
<!-- badges: end -->

Shiny apps internationalization: same app, multiple languages.

Check the full documentation at http://shi18ny.datasketch.dev


## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("datasketch/shi18ny")
```
## Your first multilanguage shiny app

This is a basic example which shows you how to solve a common problem:

```{r example}
#library(shi18ny)
## basic example code
```


## Configuration



## Add custom languages

Explore more examples.


## Roadmap

- Support RTL languages properly
- Add locale formatting for dates
- ...


## FAQ

### My language is not yet supported, what can I do to help?

File an issue and make a pull request following the instructions in the vignette.



# Acknowledgements

## Flags from

Country Flags taken from https://github.com/hjnilsson/country-flags
Catalonia flag from [wikipedia](https://meta.wikimedia.org/wiki/File:Flag_of_Catalonia.svg)




