---
title: "Getting started"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval=FALSE,
  comment = "#>"
)
```

Here we show you two different ways in which you can install the `shi18ny` package:

## To use `shi18ny` in your Shiny apps

The easiest way to use `shi18ny` to internationalize your Shiny apps and make data science more accessible across the world is by installing the package with the `devtools::install_github()` function. Note that the `devtools` package needs to be installed before you can run this function.

```{r install-github}
# install.packages("devtools")
devtools::install_github("datasketch/shi18ny")
```


## To contribute

If you want to contribute to `shi18ny` in any of the ways suggested in `vignette("contributing")`, the steps to download, build and install the package is as follows:

1. Fork the repository to your own Github account.
2. Open Git Bash and change the working directory to the location where you want the cloned repository.
3. Clone the repository from your Github account using the following command in the Git Bash:
```{git clone}
git clone https://github.com/YOUR-USERNAME/shi18ny.git
```

4. In R, set the working directory to be the file path to the folder called `shi18ny` that you just created by cloning the repository, for example:
```{r setwd}
setwd("./path/to/folder/shi18ny")
```

5. Make sure the `devtools` package is installed, and then build the package:
```{r build}
devtools::build()
```
6. You can now install the package:
```{r install}
devtools::install()
```

### Naming conventions

If you want to contribute to `shi18ny` please create a local branch based on the master branch before making any of your changes. For name of this branch, please use the following naming conventions:

* for new features: `feature/name_of_feature`
* for bug fixes: `fix/name_of_fix`
* for anything else, for example changes to the documentation: `misc/name_of_change`

